---
title: "An example of allocation on the frontier"
author: "Davide Carboni"
date: "30 May 2016"
output: html_document
---

Example of use of frontier.R this script takes symbols and find the efficient frontier 

```{r include=FALSE}
source("util.R")
source("frontier.R")

```

Lets build a portfolio with four securities
```{r}
symbols <- c("XLU","FB","AMZN","DE","CHRW", "SPY")
days=60

```


Simulate the portfolios, use 1250 samples 
```{r}
p <- simulatePortfolios(symbols,days,len=1250)
plot(p$sd,p$mean)
```


Show the lowest risk portfolios
```{r}
p <- p[p$mean>0,]#keep positive returns only
lowRisk <- p[order(p$sd),]#show low risk portfolio
head(lowRisk)
```

Show the highest return portfolios
```{r}

highRet <- p[order(p$mean,decreasing = T),]#show high return portfolios
head(highRet)
```

Select an expected return and find the portfolio with minimun risk
```{r}
q <- p[complete.cases(p),]
best <- bestPortfolio(q,expected = 0.0015)
best
```

Select an expected return and find the portfolios with best sharpe
```{r}
q$sharpe = q$mean / q$sd
head(q[order(q$sharpe),])
```


So if you have 10000$ to invest this is the best breakdown
```{r}

round(10000 * best)[,-5:-6] 
```

```{r}
n <-  length(symbols)
rets = as.returns(loadMulti(c(symbols,"SPY"),to.date = days))
rets
weights <- best[,1:n]
weights
y <- apply(rets,1,function(x){
  x <- as.numeric(x)
  sum(x[1:n] * weights)
})
rets$best <- y

d <- data.frame(Date=rets$Date,best=rets$best,SPY=rets$SPY)

equity=c(10000)
benchmark=c(10000)
for (i in 1:length(d$Date)){
  equity <- c(equity,tail(equity,1) * (1 + d$best[i]))
  benchmark <- c(benchmark,tail(benchmark,1) * (1 + d$SPY[i]))
}
equity <- head(equity,length(d$Date))
benchmark <- head(benchmark,length(d$Date))
plot(as.Date(d$Date),equity,t='l', ylim=c(min(c(equity,benchmark)),max(c(equity,benchmark))))
lines(as.Date(d$Date),benchmark,col="red")

```

