---
title: "An example of allocation on the frontier"
author: "Davide Carboni"
date: "30 May 2016"
output: html_document
---

Example of use of frontier.R this script takes symbols and find the efficient frontier 

```{r include=FALSE}
source("util.R")
source("frontier.R")

```

Lets build a portfolio with gold, SP500, Bitcoin and Japan index.
```{r}
symbols <- c("IAU","SPY","BTCUSD","EWJ")
days=90

```


Simulate the portfolios, the lower the granularity the more portfolios are simulated
```{r}
p <- simulatePortfolios(symbols,days,granularity = 0.02)
plot(p$risk,p$mean)
names(p) <- c(symbols,"risk","mean")
```


Show the lowest risk portfolios
```{r}
lowRisk <- p[order(p$risk),]#show low risk portfolio
head(lowRisk)
```

Show the highest return portfolios
```{r}

highRet <- p[order(p$mean,decreasing = T),]#show high return portfolios
head(highRet)
```

Select an expected return and find the portfolio with minimun risk
```{r}
q <- p[complete.cases(p),]
best <- bestPortfolio(q,expected = 0.00125)
best
```



